---
title: "HSB NESS Project"
output: html_document
Authors: "Reetom Gangopadhyay, Ryan Gilbert"
date: "2023-05-17"
---

## Loading Dataset
```{r corr, eval = FALSE}

df <- read.csv("data/NESS2023_hsb_data.csv")


```


## Split Dataset
```{r divide, eval = FALSE}

sensor_ids <- unique(df$sensor)

for (id in sensor_ids) {
  # Create a new dataframe for the current sensor ID
  sensor_data <- subset(df, sensors == id)
  
  # Generate a new CSV filename for the current sensor ID
  filename <- paste0("sensor_", id, ".csv")
  
  # Write the sensor data to a new CSV file
  write.csv(sensor_data, filename, row.names = FALSE)
  
  # Print the filename for confirmation
  cat("File", filename, "created.\n")
}


```



## A Few Visualizations
```{r plot}

# Load the ggplot2 package
library(ggplot2)

df1 <- read.csv("sensorData/sensor_1.csv")

# Convert the "y" column to a time series object
ts_y <- ts(df1$y)
ts_x <- ts(df1$x)

# Plot the time series
plot.ts(ts_y, main = "Time Series Plot", xlab = "Time", ylab = "Y")
abline(v=1344)
plot.ts(ts_x, main = "Time Series Plot", xlab = "Time", ylab = "X")
abline(v=1344)




```


```{r plot5}

# Load the ggplot2 package
library(ggplot2)

df5 <- read.csv("sensorData/sensor_5.csv")

# Convert the "y" column to a time series object
ts_y5 <- ts(df5$y)
ts_x5 <- ts(df5$x)

# Plot the time series
plot.ts(ts_y5, main = "Time Series Plot", xlab = "Time", ylab = "Y")
abline(v=1344)
plot.ts(ts_x5, main = "Time Series Plot", xlab = "Time", ylab = "X")
abline(v=1344)



```



```{r plot10}

# Load the ggplot2 package
library(ggplot2)

df10 <- read.csv("sensorData/sensor_10.csv")

# Convert the "y" column to a time series object
ts_y10 <- ts(df10$y)
ts_x10 <- ts(df10$x)

# Plot the time series
plot.ts(ts_y10, main = "Time Series Plot", xlab = "Time", ylab = "Y")
abline(v=1344)

plot.ts(ts_x10, main = "Time Series Plot", xlab = "Time", ylab = "X")
abline(v=1344)






```


```{r plot12}

# Load the ggplot2 package
library(ggplot2)

df12 <- read.csv("sensorData/sensor_12.csv")

# Convert the "y" column to a time series object
ts_y12 <- ts(df12$y)
ts_x12 <- ts(df12$x)
# Plot the time series
plot.ts(ts_y12, main = "Time Series Plot", xlab = "Time", ylab = "Y")
abline(v=1344)

plot.ts(ts_x12, main = "Time Series Plot", xlab = "Time", ylab = "X")
abline(v=1344)




```



```{r test1}

plot.ts(diff(df1$y))

plot.ts(diff(df1$x))

```


```{r sens5Plot}

new <- read.csv("sensorData/sensor_5.csv")

plot.ts(new$y)
abline(v=1344)

plot.ts(new$x)
abline(v=1344)

```


```{r newer}
new1 <- read.csv("sensorData/sensor_10.csv")

plot.ts(new1$y)
abline(v=1344)

plot.ts(new1$x)
abline(v=1344)





```

```{r new2}
new2 <- read.csv("sensorData/sensor_18.csv")

plot.ts(new2$y)
abline(v=1344)

plot.ts(new2$x)
abline(v=1344)

```



```{r subset}
# Read the CSV file
new <- read.csv("sensorData/sensor_5.csv")

# Subset the data for t >= 1344
subset_data <- subset(new, time >= 1344)

# Plot the 'y' variable
plot.ts(subset_data$y)
abline(v = 1344)

# Plot the 'x' variable
plot.ts(subset_data$x)
abline(v = 1344)



```

```{r ss1}

new2S <- read.csv("sensorData/sensor_18.csv")

subset2 <- subset(new2S, time >= 1344)

plot.ts(subset2$y)
abline(v=1344)

plot.ts(subset2$x)
abline(v=1344)

```


```{r ss2}

new3S <- read.csv("sensorData/sensor_10.csv")

subset3 <- subset(new3S, time >= 1344)

plot.ts(subset3$y)
abline(v=1344)

plot.ts(subset3$x)
abline(v=1344)

```



## First Lagged Regression Test

```{r lag}
library(tidyverse)
library(tsibble)
library(tidymodels)
library(dplyr)
library(feasts)
library(fable)


df1 <- read.csv("sensorData/sensor_1.csv")
df1$predCol1344 <- ifelse(df1$time >= 1344, 1, 0)
df1$predCol1345 <- ifelse(df1$time >= 1345, 1, 0)
df1$predCol1343 <- ifelse(df1$time >= 1343, 1, 0)
df1$predCol1346 <- ifelse(df1$time >= 1346, 1, 0)
df1$predCol1375 <- ifelse(df1$time >= 1375, 1, 0)


#xDiff <- diff(df1$x)
# Convert the data to tsibble format
df_tsbl1 <- df1 %>% 
  as_tsibble(key = sensor, index = time) %>%
  fill_gaps() %>%
  fill(y, x, .direction = "down")

df_split1 <- initial_time_split(df_tsbl1, prop = 96/100)
df_train1 <- training(df_split1)
df_test1 <- testing(df_split1)

model_lags_diff1 <- df_train1 %>% 
  mutate(y=c(NA,NA,NA,y[4:1336])) %>% 

model(
    lag0 = ARIMA(y ~ x),
    lag1 = ARIMA(y ~ x + lag(x)),
    lag2 = ARIMA(y ~ x + lag(x) + lag(x, 2)),
    lag3 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3)),
    lag4 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4)),
    lag5 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5)),
    lag6 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6)),
    lag7 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7)),
    lag8 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8)),
    lag9 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9)),
    lag10 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10)),
    lag11 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10) +                       lag(x, 11)),
    lag12 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10) +                       lag(x, 11) + lag(x, 12)),
    lag13 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10) +                       lag(x, 11) + lag(x, 12) + lag(x, 13)),
    lag14 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10) +                       lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14)),
    lag15 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10) +                       lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14) + lag(x, 15)),
    lag16 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10) +                       lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14) + lag(x, 15) + lag(x, 16)),
    lag17 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10) +                       lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14) + lag(x, 15) + lag(x, 16) + lag(x, 17)),
    lag18 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10) +                       lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14) + lag(x, 15) + lag(x, 16) + lag(x, 17) + lag(x, 18)),
    lag19 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10) +                       lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14) + lag(x, 15) + lag(x, 16) + lag(x, 17) + lag(x, 18) + lag(x, 19)),
    lag20 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10) +                       lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14) + lag(x, 15) + lag(x, 16) + lag(x, 17) + lag(x, 18) + lag(x, 19) +                            lag(x, 20))
  )


# View model statistics
glance(model_lags_diff1) %>%
  arrange(AICc) %>%
  select(.model:AICc)


```

## Example output for Lagged Regression
```{r mod}

#Creates the model variable to the above results
model_lag10 <- df_train1 %>% 
 model(ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10) +lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14)))


#Checking the model residuals consistency with white noise

model_lag10 %>% gg_tsresiduals()

report(model_lag10)



```


```{r forecast, eval = FALSE}
library(forecast)
library(fabletools)
library(quantmod)
library(TTR)

#Lagged Forecasts
model_pred <- forecast(model_lag10,df_test)
#Accuracy of the lagged model
cor(df_test$y,model_pred$.mean) %>% round(2)

###
# ACC = 0.29
###

```


## Function to Calculate the AICc and Perform Model Selection
```{r sensor}

library(tidyverse)
library(tsibble)
library(tidymodels)
library(dplyr)
library(feasts)
library(fable)
library(forecast)
library(fabletools)
library(quantmod)
library(TTR)

sensor_analysis <- function(sensor_number) {
  # Read the dataset
  dataset_path <- paste0("sensorData/sensor_", sensor_number, ".csv")
  df <- read.csv(dataset_path)

  # Create prediction columns
  df$predCol1344 <- ifelse(df$time >= 1344, 1, 0)
  df$predCol1345 <- ifelse(df$time >= 1345, 1, 0)
  df$predCol1343 <- ifelse(df$time >= 1343, 1, 0)
  df$predCol1346 <- ifelse(df$time >= 1346, 1, 0)
  

  # Convert the data to tsibble format
  df_tsbl <- df %>% 
    as_tsibble(key = sensor, index = time) %>%
    fill_gaps() %>%
    fill(y, x, .direction = "down")

  # Split the data into training and testing sets
  df_split <- initial_time_split(df_tsbl, prop = 96/100)
  df_train <- training(df_split)
  df_test <- testing(df_split)

  # Build the model with different lags
  model_lags_diff <- df_train %>% 
    mutate(y = c(NA, NA, NA, y[4:1336])) %>% 
    model(
      lag0 = ARIMA(y ~ x),
      lag1 = ARIMA(y ~ x + lag(x)),
      lag2 = ARIMA(y ~ x + lag(x) + lag(x, 2)),
      lag3 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3)),
      lag4 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4)),
      lag5 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5)),
      lag6 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6)),
      lag7 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7)),
      lag8 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8)),
      lag9 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9)),
      lag10 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10)),
      lag11 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10)                     + lag(x, 11)),
      lag12 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10)                     + lag(x, 11) + lag(x, 12)),
      lag13 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10)                     + lag(x, 11) + lag(x, 12) + lag(x, 13)),
      lag14 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10)                     + lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14)),
      lag15 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10)                     + lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14) + lag(x, 15)),
      lag16 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10)                     + lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14) + lag(x, 15) + lag(x, 16)),
      lag17 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10)                     + lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14) + lag(x, 15) + lag(x, 16) + lag(x, 17)),
      lag18 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10)                     + lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14) + lag(x, 15) + lag(x, 16) + lag(x, 17) + lag(x, 18)),
      lag19 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10)                     + lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14) + lag(x, 15) + lag(x, 16) + lag(x, 17) + lag(x, 18) + lag(x, 19)),
      lag20 = ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x, 10)                     + lag(x, 11) + lag(x, 12) + lag(x, 13) + lag(x, 14) + lag(x, 15) + lag(x, 16) + lag(x, 17) + lag(x, 18) + lag(x, 19)                            + lag(x, 20))
    )
  
  # View model statistics
  glance(model_lags_diff) %>%
    arrange(AICc) %>%
    select(.model:AICc)
}


```



## Apply Function to Every Subset of dataset
```{r s1}

sensor_analysis(1)

```


```{r s2}

sensor_analysis(2)

```

```{r s3}

sensor_analysis(3)

```

```{r s4}

sensor_analysis(4)

```

```{r s5}

sensor_analysis(5)

```

```{r s6}

sensor_analysis(6)

```

```{r s7}

sensor_analysis(7)

```

```{r s8}

sensor_analysis(8)

```

```{r s9}

sensor_analysis(9)

```



```{r s10}

sensor_analysis(10)

```

```{r s11}

sensor_analysis(11)

```

```{r s12}

sensor_analysis(12)

```

```{r s13}

sensor_analysis(13)

```

```{r s14}

sensor_analysis(14)

```

```{r s15}

sensor_analysis(15)

```

```{r s16}

sensor_analysis(16)

```

```{r s17}

sensor_analysis(17)

```

```{r s18}

sensor_analysis(18)

```

```{r s19}

sensor_analysis(19)

```

```{r s20}

sensor_analysis(20)

```

```{r s21}

sensor_analysis(21)

```

```{r s22}

sensor_analysis(22)

```

```{r s23}

sensor_analysis(23)

```

```{r s24}

sensor_analysis(24)

```

```{r s25}

sensor_analysis(25)

```


## Modified Function to Calculate the Accuracy Using Correlation, RMSE, MAE, and MAPE

```{r modified}

# Calculate RMSE
rmse <- function(actual, predicted) {
  sqrt(mean((actual - predicted)^2))
}

# Calculate MAE
mae <- function(actual, predicted) {
  mean(abs(actual - predicted))
}

# Calculate MAPE
mape <- function(actual, predicted) {
  mean(abs((actual - predicted) / actual)) * 100
}

new_model <- function(sensor_number,optimal) {
  # Read the dataset
  dataset_path <- paste0("sensorData/sensor_", sensor_number, ".csv")
  df <- read.csv(dataset_path)

  # Convert the data to tsibble format
  df_tsbl <- df %>% 
    as_tsibble(key = sensor, index = time) %>%
    fill_gaps() %>%
    fill(y, x, .direction = "down")

  # Split the data into training and testing sets
  df_split <- initial_time_split(df_tsbl, prop = 96/100)
  df_train <- training(df_split)
  df_test <- testing(df_split)
  
  #x <- 0
  if (optimal == 0) {
    x <- ARIMA(y ~ x)
  } else if (optimal == 1) {
    x <- ARIMA(y ~ x + lag(x))
  } else if (optimal == 2) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2))
  } else if (optimal == 3) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3))
  } else if (optimal == 4) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4))
  } else if (optimal == 5) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5))
  } else if (optimal == 6) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x,6))
  } else if (optimal == 7) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x,6) + lag(x,7))
  } else if (optimal == 8) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x,6) + lag(x,7) + lag(x,8))
  } else if (optimal == 9) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9))
  } else if (optimal == 10) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10))
  } else if (optimal == 11) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11))
  } else if (optimal == 12) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12))
  } else if (optimal == 13) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13)) 
  } else if (optimal == 14) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13) + lag(x,14))
  } else if (optimal == 15) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13) + lag(x,14) + lag(x,15))
  } else if (optimal == 16) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13) + lag(x,14) + lag(x,15) + lag(x,16))
  } else if (optimal == 17) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13) + lag(x,14) + lag(x,15) + lag(x,16) + lag(x,17))
  } else if (optimal == 18) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13) + lag(x,14) + lag(x,15) + lag(x,16) + lag(x,17) + lag(x,18))
  } else if (optimal == 19) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13) + lag(x,14) + lag(x,15) + lag(x,16) + lag(x,17) + lag(x,18) + lag(x,19))
  } else if (optimal == 20) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13) + lag(x,14) + lag(x,15) + lag(x,16) + lag(x,17) + lag(x,18) + lag(x,19) + lag(x,20))
  } else if (optimal == 21) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13) + lag(x,14) + lag(x,15) + lag(x,16) + lag(x,17) + lag(x,18) + lag(x,19) + lag(x,20) +                         lag(x,21))
  } else if (optimal == 22) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13) + lag(x,14) + lag(x,15) + lag(x,16) + lag(x,17) + lag(x,18) + lag(x,19) + lag(x,20) +                         lag(x,21) + lag(x,22))
  } else if (optimal == 23) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13) + lag(x,14) + lag(x,15) + lag(x,16) + lag(x,17) + lag(x,18) + lag(x,19) + lag(x,20) +                         lag(x,21) + lag(x,22) + lag(x,23))
  } else if (optimal == 24) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13) + lag(x,14) + lag(x,15) + lag(x,16) + lag(x,17) + lag(x,18) + lag(x,19) + lag(x,20) +                         lag(x,21) + lag(x,22) + lag(x,23) + lag(x,24))
  } else if (optimal == 25) {
    x <- ARIMA(y ~ x + lag(x) + lag(x, 2) + lag(x, 3) + lag(x, 4) + lag(x, 5) + lag(x, 6) + lag(x, 7) + lag(x, 8) + lag(x, 9) + lag(x,10) +                    lag(x,11) + lag(x,12) + lag(x,13) + lag(x,14) + lag(x,15) + lag(x,16) + lag(x,17) + lag(x,18) + lag(x,19) + lag(x,20) +                         lag(x,21) + lag(x,22) + lag(x,23) + lag(x,24) + lag(x,25))
  } else {
    print("Enter valid model number")
  }
  
  #Creates the model variable to the above results
  model_lag <- df_train %>% 
  model(x)

  #Lagged Forecasts
  model_pred <- forecast(model_lag,df_test)
  #Accuracy of the lagged model
  corr <- cor(df_test$y,model_pred$.mean)
  rmse_value <- rmse(df_test$y, model_pred$.mean)
  mae_value <- mae(df_test$y, model_pred$.mean)
  mape_value <- mape(df_test$y, model_pred$.mean)
  
  return(c(corr,rmse_value,mae_value,mape_value))
    
}


```



```{r m1}

new_model(1,14)

```

```{r m2}

new_model(2,12)

```

```{r m3}

new_model(3,2)

```

```{r m4}

new_model(4,0)

```

```{r m5}

new_model(5,0)

```

```{r m6}

new_model(6,0)

```

```{r m7}

new_model(7,0)

```

```{r m8}

new_model(8,2)

```

```{r m9}

new_model(9,1)

```

```{r m10}

new_model(10,3)

```

```{r m11}

new_model(11,5)

```

```{r m12}

new_model(12,3)

```

```{r m13}

new_model(13,1)

```

```{r m14}

new_model(14,3)

```

```{r m15}

new_model(15,0)

```

```{r m16}

new_model(16,3)

```

```{r m17}

new_model(17,0)

```

```{r m18}

new_model(18,3)

```

```{r m19}

new_model(19,5)

```

```{r m20}

new_model(20,8)

```

```{r m21}

new_model(21,9)

```

```{r m22}

new_model(22,0)

```

```{r m23}

new_model(23,6)

```

```{r m24}

new_model(24,3)

```

```{r m25}

new_model(25,0)

```


```{r table}

corr_ <- c(0.2850156, -0.1985804,0.4317807,-0.5727044,-0.9351473,0.6979605,0.2397834,0.8213864,0.8628446,0.7244551,0.7025885,-0.6145417 ,-0.2372313,-0.1572974,-0.4290279,0.8820703,0.6035457,0.7286345,0.8773727,-0.1330419,0.029318,-0.6161878,0.3651865,-0.07735744,-0.5941115)

rmse_ <- c(2.8902866,0.5186161,2.0747828,1.3670535,4.6727013,0.3655833,1.5898714,0.2139970,0.1803793,0.3871408,0.1415618,4.1074746,0.7657854,0.7874627,1.2048452,0.5006987,0.6961931,0.3601709,0.8773727,0.9788590,2.978385,4.7265013,1.8310004,1.16441358,5.2124045)

mae_ <- c(2.3890621,0.4732088,1.6982856,1.1634933,3.8317851,0.3204187,1.2315587,0.1667468,0.1511331,0.3489035,0.1200196,3.4704062,0.4901594,0.4703228,0.9817399,0.4551038,0.4769033,0.2534484,0.4873389,0.8349040,2.556157,4.0286755,1.6175979,0.74143187,4.3663814)

mape_ <- c(133.1807841,20.8518168,1510.8063642,1073.2308270,1101.8823363,23.7744373,284.0233381,12.6087802,6.3912964,9.9190683,9.4057180,133.1220172,25.8644374,155.1356787,668.6410292,43.2512936,43.9597054,25.0217593,183.7186666,218.2972510,425.927647,150.6970522,3280.8653627,233.33718108,284.1579113)

error_df <- data.frame(sensor=1:25,
                       corr=corr_,
                       rmse=rmse_,
                       mae=mae_,
                       mape=mape_)

error_df

```


```{r histo}

library(ggplot2)

ggplot(error_df, aes(x = factor(sensor), y = rmse)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(x = "Sensor", y = "RMSE") +
  ggtitle("RMSE by Sensor")

ggplot(error_df, aes(x = factor(sensor), y = mae)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(x = "Sensor", y = "MAE") +
  ggtitle("MAE by Sensor")


ggplot(error_df, aes(x = factor(sensor), y = mape)) +
  geom_bar(stat = "identity",fill = "steelblue") +
  labs(x = "Sensor", y = "MAPE") +
  ggtitle("MAPE by Sensors")


```




## Analysis

The analysis involved splitting the data into training and testing samples for each sensor. The training samples include the observations from 1 to 1336 which is before the event and the testing sample was the rest of the dataset. Note that the train/test split is done for each of the 25 sensors individually.

The model used is a lagged regression model with a ARMA error given by $$Y_t = \beta_0 + \beta_1*x_t-1 +\beta_2*x_t-2...\beta_l*x_t-l + 	\eta_t$$. The order of the model was selected by the AICc criterion. 

Model diagnostics were carried out to determine the adequacy of the model. The fitted model model is used to forecast for the test sample and the accuracy of the forecast was determined using Correlation, RMSE, MAE, and MAPE.

Generally, if there is no action taken after the alert, you expect no structural changes to the time series and the forecast will return a low value of RMSE, MAE, and MAPE. On the other hand, if action is taken, you expect a very high value for each of these metrics as the forecast will fail to properly model the values of the time series after the alert.

Based on the MAE/RMSE we chose cutoffs of the following:

MAE: 1.5
RMSE: 1.5

Meaning that the action was taken after the alerts for the following sensors:

RMSE: 1,3,5,7,12,21,22,23,25

MAE: 1,3,5,12,21,22,23,25

Since 7 is not in both of these metrics the final set is the following:

Action Taken: 1,3,5,12,21,22,23,25










